Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-30 prob.tex
prob.tex \section{Proof} Updating...

\begin{definition}For any continuous function~$f:S^{d-1}\rightarrow\mathbb{R}$,
the modulus of continuity of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}

\begin{definition}For any continuous function~$f:S^{d-1}\rightarrow\mathbb{R}$,
the modulus of continuity of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}

\begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
is a frame function of weight~$\left(W_{l},W_{r}\right)$, and $\ket{\psi}\in S^{2}$,
then the \emph{symmetrization} of $f$ with respect to $\ket{\psi}$
is the function~$g:S^{2}\rightarrow\mathbb{R}$ defined by
\[
g\left(\ket{\phi}\right)=f\left(\ket{\phi}\right)+f\left(\sigma\ket{\phi}\right)
\]
where $\sigma$ is clockwise rotation by $\pi/2$ about $\ket{\psi}$.\qed\end{definition}

The following theorem is an analog to Corollary 22 in \cite{RichmanBridges1999}.

\begin{thm}Let $f$ be an bounded continuous frame function of weight~$\left(W_{l},W_{r}\right)$,
$m=\inf f$ or $m=\sup f$, and $W=\left(W_{l}+W_{r}\right)/2$. Let
$Q$ be the quadratic form given by
\[
Q\left(\ket{\phi}\right)=W-m+\left(3m-W\right)\ip{\psi}{\phi}^{2}=2m\ip{\psi}{\phi}^{2}+\left(W-m\right)\left(1-\ip{\psi}{\phi}^{2}\right)
\]
For each $\delta>0$, there is $\eta>0$ such that if
\begin{itemize}
\item $\ket{\psi}\in S^{2}$such that $\left|f\left(\ket{\psi}\right)-m\right|<\eta$,
and 
\item $g$ is the symmetrization of $f$ with respect to $\ket{\psi}$.
\end{itemize}
then $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le\delta+3\left(W_{r}-W_{l}\right)\left[12\left\lceil \frac{\pi^{2}}{\omega_{f}^{-1}\left(\frac{\delta}{36}\right)}\right\rceil +1\right]$,
where $\left\lceil x\right\rceil $, ceiling function~\cite{GrahamKnuthPatashnik1994,PurdomBrown1995},
is the smallest integer not less than $x$.\qed\end{thm}

We can see that for a

>>>>

\begin{definition}\cite{CourantJohn1965,Voevodskyothers2013}~For
any function~$f$, a function~$\varDelta_{f}:\left(0,\infty\right]\rightarrow\left(0,\infty\right]$
is a modulus of continuity of $f$ if for every $\epsilon>0$, $\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\varDelta_{f}\left(\epsilon\right)$
implies $\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|<\epsilon$.\qed\end{definition}

Notice that a function $f$ may have more than one modulus of continuity.
For example, $\varDelta_{f}\left(\epsilon\right)=\frac{\epsilon}{2}$
and $\epsilon$ are both modulus of continuity of $f\left(\ket{\psi}\right)=\left|\ip{\psi}{0}\right|^{2}$
on $S^{2}$. Conversely, a function may be a modulus of continuity
of two different functions. For example, $\varDelta\left(\epsilon\right)=\frac{\epsilon}{2}$
is a modulus of continuity of both $f\left(\ket{\psi}\right)=\left|\ip{\psi}{0}\right|^{2}$
and $f\left(\ket{\psi}\right)=\frac{1}{3}$ on $S^{2}$.

\begin{definition}\cite{RichmanBridges1999}~If $f:S^{2}\rightarrow\mathbb{R}$
is a approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
and $\ket{\psi}\in S^{2}$, then the \emph{symmetrization} of $f$
with respect to $\ket{\psi}$ is the function~$g:S^{2}\rightarrow\mathbb{R}$
defined by
\[
g\left(\ket{\phi}\right)=f\left(\ket{\phi}\right)+f\left(\sigma\ket{\phi}\right)
\]
where $\sigma$ is clockwise rotation by $\pi/2$ about $\ket{\psi}$.\qed\end{definition}

The following theorem is an analog to Corollary~22 in \cite{RichmanBridges1999}.
The only significant difference is that we assume the approximation
frame function is continuous. The approximation frame function might
not be continuous as in all of our previous example, while the frame
function in original Gleason's theorem is always continuous. Thus,
we need to assume the continuity to follow the proof in \cite{RichmanBridges1999}.

\begin{thm}\label{thm:analogCorollary22RichmanBridges1999}Let $f$
be an bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$m=\inf f$ or $m=\sup f$, and $W=\left(W_{l}+W_{r}\right)/2$. Let
$Q$ be the quadratic form given by
\[
Q\left(\ket{\phi}\right)=W-m+\left(3m-W\right)\ip{\psi}{\phi}^{2}=2m\ip{\psi}{\phi}^{2}+\left(W-m\right)\left(1-\ip{\psi}{\phi}^{2}\right)
\]
For each $\delta>0$, there is $\eta>0$ such that if
\begin{itemize}
\item $\ket{\psi}\in S^{2}$such that $\left|f\left(\ket{\psi}\right)-m\right|<\eta$,
and 
\item $g$ is the symmetrization of $f$ with respect to $\ket{\psi}$.
\end{itemize}
then $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le\delta+3\left(W_{r}-W_{l}\right)\left[12\left\lceil \frac{\pi^{2}}{\varDelta_{f}\left(\frac{\delta}{36}\right)}\right\rceil +1\right]$,
where $\left\lceil x\right\rceil $, ceiling function~\cite{GrahamKnuthPatashnik1994,PurdomBrown1995},
is the smallest integer not less than $x$.\qed\end{thm}

Since $\delta$ can be arbitrary small in theorem~\ref{thm:analogCorollary22RichmanBridges1999},
we can get the following corollary.

\begin{cor}Let $f$ be a bounded continuous approximation frame function
of weight~$\left(W_{l},W_{r}\right)$, $m=\min f=f\left(\ket{\psi}\right)$
or $m=\max f=f\left(\ket{\psi}\right)$, and $W=\left(W_{l}+W_{r}\right)/2$.
Let $Q$ be the quadratic form given by
\[
Q\left(\ket{\phi}\right)=W-m+\left(3m-W\right)\ip{\psi}{\phi}^{2}=2m\ip{\psi}{\phi}^{2}+\left(W-m\right)\left(1-\ip{\psi}{\phi}^{2}\right)
\]
If $g$ is the symmetrization of $f$ with respect to $\ket{\psi}$,
then $\left|Q\left(\ket{\phi}\right)-g\left(\ket{\phi}\right)\right|\le3\left(W_{r}-W_{l}\right)$.\qed\end{cor}

Corollary~22 in \cite{RichmanBridges1999} is used to prove theorem~23
which is the final step to prove Gleason's theorem in \cite{RichmanBridges1999}.
Theorem~23 reads as the following.

\begin{thm}Let $f$ be a bounded frame function on the unit sphere
in $\mathbb{R}^{3}$, and $\delta>0$. Then there is a quadratic form
$Q$ on $\mathbb{R}^{3}$ so that $\left|f\left(x\right)-Q\left(x\right)\right|\le3\delta$
for all $\ket{\phi}$ on the sphere.\qed\end{thm}

Currently, we can only prove the following.
